|

### 2023-03-23 paper/02-data.Rmd
Initial draft of data section with table and figure ideas

We rely on Next Gen Stats data provided by the 2023 NFL Big Data Bowl competition [@Howard2023NFL] for our investigation.
The data span the first eight weeks of the 2021 NFL regular season, consisting of a total of 122 games.
Also included are general information about the players, games, and plays within each game
At a more granular level, we are given information on the player and football locations recorded at 10 frames per second for each play.
Also included are scouting data supplied by Pro Football Focus, which collects player-level information at the play level.

>>>>

We use the tracking data made available in the 2023 NFL BDB competition for our investigation. The data corresponds to _INSERT NUMBER_ passing plays across 122 games in the first eight weeks of the 2021 NFL regular season. The aforementioned NGS data provides the on-field location, speed, direction, and orientation of each player on the field (and the ball) at a rate of 10 Hz, along with event annotations (e.g., ball snapped, pass thrown, etc.). In this particular dataset, there are _INSERT NUMBER_ unique frames corresponding to moments of time from the start of the play at snap until the moment the quarterback either throws the pass or is sacked. (_VERIFY THIS STATEMENT MAKES SENSE_)

_Table X_ displays example data for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ended with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack]. _Figure X_ presents the locations of every Las Vegas (black) and Denver (orange) player on the field at four particular moments of time, with Maxx Crosby highlighted (blue).

_INSERT TABLE_

_INSERT FIGURE_

Along with the tracking information, the 2023 BDB includes scouting data provided by Pro Football Focus (PFF). PFF's scouting data includes manually collected player-level information at the play level, such as the player's role (e.g., if they are a pass rusher) and credited events (e.g., player is credited with hitting the QB on the play). In this manuscript, we use the PFF data to identify _INSERT NUMBER_ unique players designated in the "pass rush" role across all plays. For context, _Figure X_ displays the distribution of the number of observed pass rushers involved in a play, ranging from _INSERT NUMBER_ to _INSERT NUMBER_ with _INSERT NUMBER_ pass rushers as the most common value. We also leverage the PFF data to count how many hits, hurries, and sacks each pass rusher is credited with across span of collected data. Additionally, we use the PFF player roles to identify which players were labeled as blocking each pass rusher to adjust for opponent strength, as discussed in Section _INSERT NUMBER_.

INSERT FIGURE
